# Research Paper: "Validated Digital Literacy Measures for Populations with Low Levels of Internet Experiences"
# Authors: Dr. Ayesha Ali, Dr. Agha Ali Raza, and Dr. Ihsan Ayyub Qazi
# R code: This code provides a trained Random Forest (RF) model for predicting the digital literacy of users using the best 7-item survey module (referred to as platform-neutral module in the paper).
# Note: For any questions or comments, please email ihsan.qazi@lums.edu.pk

# The 7 questions in the survey module and their response options are as follows:
#   1. Are you able to search/google things online? Yes(1); No(0)
#   How familiar are you with the following computer and Internet-related items? Please choose a number
#   between 1 and 5, where 1 represents no understanding and 5 represents full understanding of the item:
#   2. Internet 1-5
#   3. Browser 1-5
#   4. PDF 1-5
#   5. Bookmark 1-5
#   6. URL 1-5
#   7. Torrent 1-5

# Model Card
# Input: one or more observations, where each observation correponds to responses to the 7 questions above
# Input Order: (term_pdf, term_internet, term_browser, term_bookmark, term_url, research, term_torrent) - See example below.
# Output: for each observation the model predicts a digital literacy score between 0 and 1
# Model: A random forest model trained using 100,000 trees. We used the randomForest library in R and employed default values for other hyperparameters.
# Model Performance: R^2 over OOB samples was 0.8 and MSE was 0.019
# Data: The model was trained over a sample of 143 individuals from Pakistan with different levels of digital literacy (please refer to the paper for a detailed description of the model)
# Suitability: The model is best suited for populations comprising a high proportion of individuals with low levels of digital literacy.


```{r}
library(randomForest)
library(caret)
library(e1071)
library(tidyr)
```


**Predict digital literacy of new samples** 
```{r}

# load the model
rf_model <- readRDS("./rf_model.rds")

# print model details
print(rf_model)

# create new samples, where each sample if a 7-tuple (L below refers to an integer so 4L means the response was 4)
# inpur order: (term_pdf, term_internet, term_browser, term_bookmark, term_url, search, term_torrent)
a <- c(4L,4L,4L,3L,4L,1L,4L)
b <- c(3L,3L,3L,2L,3L,0L,1L)
c <- c(1L,1L,2L,2L,2L,0L,1L)

# create a data frame and name columns
new_df<- data.frame()
new_df<- rbind(new_df, a)
new_df<- rbind(new_df, b)
new_df<- rbind(new_df, c)
names(new_df) <- c('term_pdf', 'term_internet', 'term_browser', 'term_bookmark', 'term_url', 'search', 'term_torrent')
new_df

# predict the digital literacy
y_predict <- predict(rf_model,new_df)
print("Predicted Digital Literacy Score:")
y_predict

#write.table(y_predict, file = “output_prediction.txt”) 
```